Trail Saving on Backtrack

### 2020-02-22 paper.tex
typo

\begin{document}
\maketitle
\begin{abstract}
    A CDCL \sat solver can backtrack a large distance when it learns a
    new clause, e.g, when the new learnt clause is a unit clause the
    solver has to backtrack to level zero. When the length of the
    backtrack is large the solver can end up reproducing many of the
    same decisions and propagations when it redescent the search
    tree. Motivated by this potential redundancy, partial backtracking
    (chronological backtracking) has been proposed. This technique
    allows the solver to reduce the length of its backtrack, e.g.,
    allowing the solver to backtrack to the previous level after a
    conflict is found. However, this technique has its shortcomings
    and only tends to work when limits are placed on its
    application. In this paper we present a new trail saving technique
    that makes a copy of the part of the trail that was backtracked
    over. This saved copy can then be used to improve the efficiency
    of the solver's subsequent redescent. Although our technique does
    not save as much work as chronological backtracking it also does
    not have chronological backtracking's shortcomings. Furthermore,
    the saved trail also provides the solver the ability to look ahead
    along the previous trail. This can be exploited to improve its
    efficiency. Our empirical results show that our technique often
    yields superior performance over chronological backtracking, and
    that is is able to improve the performance of state of the art
    solvers.

>>>>

\begin{document}
\maketitle
\begin{abstract}
    A CDCL \sat solver can backtrack a large distance when it learns a
    new clause, e.g, when the new learnt clause is a unit clause the
    solver has to backtrack to level zero. When the length of the
    backtrack is large, the solver can end up reproducing many of the
    same decisions and propagations when it redescends the search
    tree. Motivated by this potential redundancy, partial backtracking
    (chronological backtracking) has been proposed. This technique
    allows the solver to reduce the length of its backtrack, e.g.,
    allowing the solver to backtrack to the previous level after a
    conflict is found. However, this technique has its shortcomings
    and only tends to work when limits are placed on its
    application. In this paper we present a new trail saving technique
    that makes a copy of the part of the trail that was backtracked
    over. This saved copy can then be used to improve the efficiency
    of the solver's subsequent redescent. Although our technique does
    not save as much work as chronological backtracking, it also does
    not have chronological backtracking's shortcomings. Furthermore,
    the saved trail also provides the solver the ability to look ahead
    along the previous trail. This can be exploited to improve its
    efficiency. Our empirical results show that our technique often
    yields superior performance over chronological backtracking, and
    that is is able to improve the performance of state of the art
    solvers.
